---
title: "Vector types"
format:
  html:
    embed-resources: true
    toc: true
execute:
  warning: false
editor_options: 
  chunk_output_type: console
editor: visual
---

```{r}
#| label: setup

library(tidyverse)
library(nycflights13)
```

## Task 1: Numeric vector

1.  Create a numeric vector using `c()` with the numbers from 1, 2, 3, 4, 5 to 10. Run the code.

2.  Create a numeric vector using `seq(1, 10)` and run the code.

3.  What's the difference between the two vectors?

```{r}
c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)

seq(1, 10)
```

## Task 2: Character vector

1.  Create a character vector using `c()` with the letters from "a" to "f". Run the code.

2.  On a new line, write `letters` and run the code. What's stored in the `letters` object?

3.  On a new line, write `?letters` and run the code. What did you learn?

```{r}

c("a", "b", "c", "d", "e", "f")

letters
```

## Task 3: Numeric sequences

1.  Create a numeric vector using `seq(1, 100, 1)` and run the code. What does the code do?

2.  Create a numeric vector using `runif(100, 1, 100)` and run the code. What does the code do?

3.  Create a numeric vector using `sample(1:100, 100, replace = FALSE)` and run the code. What does the code do?

```{r}

seq(1, 100, 1)

runif(100, 1, 100)

sample(1:100, 100, replace = FALSE)

seq_along(letters)

```

## Task 4: Numeric sequences along a character vector

1.  Create a numeric vector using `seq_along(letters)` and run the code. What does the code do?

2.  Create a character vector using `month.name` and run the code. What does the code do?

3.  Create a numeric vector using `seq_along(month.name)` and run the code. What does the code do?

```{r}
seq_along(letters)

month.name

seq_along(month.name)

```

## Task 5: Distribution of random numbers

1.  Create a numeric vector `runif(n = 1000, min = 1, max = 100)  |> hist()` and run the code. What does the code do? Remove `|> hist()` and run the code again. What does the code do?

2.  Create a numeric vector `rnorm(n = 1000, mean = 500, sd = 150) |> hist()` and run the code. What does the code do? Remove `|> hist()` and run the code again. What does the code do?

```{r}

runif(n = 1000, min = 1, max = 100) |> hist()

rnorm(n = 1000, mean = 500, sd = 150) |> hist()
```

## Task 6: Logical vectors

1.  Create a numeric vector using `rnorm(n = 1000, mean = 50, sd = 5)` and use the assignment operator to store it in an object called `norm100`. Run the code.

2.  Write:

-   `mean(norm100)` and run the code. What does the code do?
-   `norm100 >= 50` and run the code. What does the code do?
-   `sum(norm100 >= 50)` and run the code. What does the code do?
-   `mean(norm100 >= 50)` and run the code. What does the code do?

```{r}

norm_dist <- rnorm(n = 1000, mean = 50, sd = 5) 

mean(norm_dist)

norm_dist >= 50

sum(norm_dist >= 50)

mean(norm_dist >= 50)

```

## Task 7 (stretch goal)

In this task, we will use the `flights` data object of the `nycflights13` package. The `flights` data object contains information about all flights that departed from NYC (e.g., EWR, JFK and LGA) in 2013. The data object contains 336,776 rows and 19 columns.

1.  Use the `flights` data object with `mutate()` to create `delayed`, a variable that displays whether a flight was delayed (`arr_delay > 0`).

2.  Use relocate to move `delayed` to the front of the data frame. Run the code. What vector type is the `delayed` variable?

3.  Then, remove all rows that contain an NA in `delayed`.

4.  Finally, create a summary table with `summarise()` that shows

-   How many flights were delayed
-   What proportion of flights were delayed

```{r}

flights |> 
  mutate(delayed = arr_delay > 0) |> 
  relocate(delayed) |> 
  filter(!is.na(delayed)) |> 
  summarise(sum = sum(delayed),
            prop = mean(delayed))
```
